Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-15 paper/paper.tex
Turn graphs back on
Consistent ordering for thanks and inst
we don't need no stinking CRLFs
funding acks

\author{
    Lars Kotthoff\inst{1}
    \and Ciaran McCreesh\thanks{This work was supported by the Engineering
        and Physical Sciences Research Council [grant number EP/K503058/1]}\inst{2}
    \and Christine Solnon\inst{3}\thanks{This work has been supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01).}}

@@

\begin{figure}[!ht]
%\includegraphics[width=\textwidth]{figures/portfolio-ecdf}
\caption{Empirical cumulative distribution function of solvers, virtual best
solvers, and the \LLAMA portfolio on the reduced set of 2336 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf}
\end{figure}

@@

\begin{figure}[!ht]
%\includegraphics[width=\textwidth]{figures/portfolio-ecdf-full}
\caption{Empirical cumulative distribution function of solvers, virtual best
solvers, and the portfolio system on the full set of 5725 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf-full}
\end{figure}

>>>>

\author{
    Lars Kotthoff\thanks{This work was supported by an NSERC E.W.R.\ Steacie
    Fellowship and under the NSERC Discovery Grant Program.}\inst{1}
    \and Ciaran McCreesh\thanks{This work was supported by the Engineering
        and Physical Sciences Research Council [grant number EP/K503058/1]}\inst{2}
    \and Christine Solnon\thanks{This work has been supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01).}\inst{3}}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/portfolio-ecdf}
\caption{Empirical cumulative distribution function of solvers, virtual best
solvers, and the \LLAMA portfolio on the reduced set of 2336 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/portfolio-ecdf-full}
\caption{Empirical cumulative distribution function of solvers, virtual best
solvers, and the portfolio system on the full set of 5725 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf-full}
\end{figure}
